Untitled

### 2023-08-11 draft_v0.Rmd
Exploration started. From Windows.

# libraries
library(tidyverse)

@@

unique(dta$section)
glimpse(dta)
```

@@

@@

@@

```{r overview}

dta %>% 
  select(directorate) %>% 
  arrange(directorate) %>% 
  distinct()

# missing directorate

dta %>% 
  filter(!complete.cases(dta)) %>% 
  group_by(is.na(.)) %>% 
  count() %>% 
  print(n = Inf)

dta %>% 
  filter(is.na(directorate)) %>% 
  select(-contains(c("number", "stamp", "year", "month")), -longitude, -latitude) %>% 
  distinct() %>% 
  print(width = Inf)
  group_by(official_suburb) %>% 
  count() %>% 
  arrange(desc(n))

>>>>

# libraries
library(kableExtra)
library(knitr)
library(tidyverse)

@@

# dates

@@

# missing directorate and dates

unique(dta$month_creation)

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, is.na(directorate)) %>% 
               count(name = "n_missing")) %>%
  ungroup() %>% 
  rename(missing_directorate = 4) %>% 
  filter(missing_directorate == TRUE) %>% 
  mutate(percentage_missing = n_missing/total_ym*100) %>% 
  kable() %>%
  kable_styling(full_width = FALSE, position = "left")

@@

# Exclude if missing directorate

dta <- dta %>% 
  filter(!is.na(directorate))

# Missingness in urban mobility
unique(dta$directorate)

dta_um <- dta %>% 
  filter(directorate == "URBAN MOBILITY")

x <- which(names(dta_um) %in% c("code_group", "code", "cause_code_group", "cause_code"))

map(dta_um[x], ~sort(unique(.x))) 
map(dta_um[x], ~sum(is.na(.x)))

dta_um %>%
  select(all_of(x)) %>% 
  group_by(is.na(.)) %>% 
  count()

x <- nrow(dta_um)

x1 <- dta_um %>% 
  group_by(is.na(cause_code_group), is.na(cause_code)) %>% 
  count(name = "missing_cause") %>% 
  ungroup() %>% 
  rename(...1 = 1, ...2 = 2) %>% 
  filter(...1 == TRUE & ...2 == TRUE) %>% 
  pull(missing_cause)

tibble(msg = glue::glue("Missing cause for {round(x1/x*100, 2)}% of entries.")) %>% 
  kable(col.names = NULL) %>%
  kable_styling(full_width = FALSE, position = "left")

@@

```{r overview}
x <- nrow(dta)

dta %>% 
  group_by(directorate) %>% 
  count(name = "Nr_of_entries") %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/x*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  kable(title = "Number and percentage of entries per Directorate") %>%
  kable_styling(full_width = FALSE, position = "left")

dta %>% 
  group_by(year_creation, month_creation) %>% 
  count(name = "total_ym") %>% 
  inner_join(dta %>% 
               group_by(year_creation, month_creation, directorate) %>% 
               count(name = "Nr_of_entries")) %>% 
  ungroup() %>% 
  mutate(Percentage_of_total = round(Nr_of_entries/total_ym*100, 2)) %>% 
  arrange(desc(Nr_of_entries)) %>% 
  ggplot(aes(month_creation, Percentage_of_total, 
             fill = reorder(directorate, Percentage_of_total)))+
  geom_col()+
  facet_wrap(~year_creation, scales = "free_x") # resize left bar?
